Fusing Filters with Integer Linear Programming

### 2014-05-14 2014betterfusionforfilters/section/05-Benchmarks.tex
explanation of quickhull clustering

\subsection{Quickhull}
Is Quickhull any better? Seems like it's just one cluster; @filterMax@. And we don't have append (@++@), anyway.
\begin{code}
quickhull :: Vec Pt -> Vec Pt
quickhull pts
 = let top  = fold getTop pts
       bot  = fold getBot pts
       tops = hull (top,bot) pts
       bots = hull (bot,top) pts
   in  tops ++ bots

hull :: (Pt,Pt) -> Vec Pt -> Vec Pt
hull line@(l,r) pts
 = let pts' = filter (above   line) pts
       ma   = fold   (maxFrom line) pts'
       hl   = hull   (l, ma)        as
       hr   = hull   (ma, r)        as
   in  hl  ++ hr
\end{code}

>>>>

\subsection{QuickHull}
The core of the QuickHull algorithm is very similar to @hull@, below.
Given a line and an array of points, the points are filtered to those above the line,
and the farthest point above the line is also found.

\begin{code}
hull :: (Point,Point) -> Array Point -> Array Point
hull line@(l,r) pts
 = let pts' = filter (above   line) pts
       ma   = fold   (maxFrom line) pts'
       hl   = hull   (l, ma)        pts'
       hr   = hull   (ma, r)        pts'
   in  hl  ++ hr
\end{code}

Stream fusion is unable to fuse the @pts'@ and @ma@ together, as @pts'@ is used multiple times and cannot be inlined into @ma@.
Similarly, Megiddo~\cite{megiddo1998optimal} is unable to fuse them together, as their iteration sizes are different.
Our formulation is able to fuse these together.

If the @fold@ is changed to operate over @pts@ instead of @pts'@, Megiddo's formulation \emph{is} able to fuse the two.
Interestingly, a programmer unaware of fusion would expect the original version to be faster, because @pts'@ is smaller than @pts@.

\begin{code}
 = let pts' = filter (above   line) pts
       ma   = fold   (maxFrom line) pts
\end{code}
